Hydras \& Co.

### 2022-01-30 doc/gaia-chapter.tex
add a few lemmas
fix a typo
Import lemmas from theories/ordinal/Epsilon0/Canon (clumsy, partial) (#115)
* Import lemmas from theories/ordinal/Epsilon0/Canon (clumsy, partial)

* minor changes (SSreflect style)

* simplification of rewritings from hydras to gaia (init)

* fix an error in gaia-chapter.tex

* Simplify some ports in Bridge

* minor changes
new snippets for gaia-hydras

\inputsnippets{T1Bridge/iotaPiDef}

\inputsnippets{T1Bridge/iotaPiRw, T1Bridge/piIotaRw}

@@

\inputsnippets{T1Bridge/utf8try}

@@

\subsubsection{Porting a theorem}
The \texttt{Gaia} library containsa proof that the multiplication of ordinals less than $\epsilon_0$ is associative.

@@

\inputsnippets{T1Bridge/gE0iotaPi}

@@

>>>>

\inputsnippets{T1Bridge/h2gG2hDef}

\inputsnippets{T1Bridge/h2gG2hRw, T1Bridge/g2hH2gRw}

@@

%\inputsnippets{T1Bridge/utf8try}

@@

@@

\inputsnippets{T1Bridge/gE0h2gG2h}

@@

\section{Porting theorems without big effort}

\subsection{Porting a theorem from \gaia}
The \texttt{Gaia} library contains a proof that the multiplication of ordinals less than $\epsilon_0$ is associative.

\subsection{Porting theorems from \Hydras}

\subsubsection{Canonical sequences}

In~\href{../theories/html/gaia_hydras.GCanon.html}%
{\texttt{gaia\_hydras.GCanon}}, canonical sequences are just imported from the library \linebreak
\href{../theories/html/hydras.Epsilon0.Canon.html}%
{\texttt{hydras.Epsilon0.Canon}}.

First, we rename \Hydras's \texttt{canon} function into
\texttt{hcanon}. Then we define a new function \emph{via} the
translations \texttt{g2h} and \texttt{h2g}.

\inputsnippets{GCanon/canonDef}

\begin{todo}
Explain the proof !
\end{todo}

\inputsnippets{GCanon/gcanonLimitOf}
